---
title: "Data Modeling using Merged Data Set"
date: '2022-06-27'
output: pdf
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(corrplot)
library(dplyr)
```

```{r}

#Load data sets
df.orders = read.csv('./data/orders_clean.csv',header=TRUE)
df.vendors = read.csv('./data/vendors_clean.csv',header=TRUE)

#Average Speed per hour calculated using available data on Pickup Times, Delivery times and Delivery distances. See: data_average_speed.Rmd
avg_speed = 35.83
df.orders$delivery_time = df.orders$deliverydistance * avg_speed

#Create new indicator variables based on Location Type column
df.orders = df.orders %>%
            mutate(Loc_Home = ifelse(LOCATION_TYPE=="Home",1,0)) %>%
            mutate(Loc_Work = ifelse(LOCATION_TYPE=="Work",1,0)) %>%
            mutate(Loc_Other = ifelse(LOCATION_TYPE=="Other",1,0))

#Calculate Averages of deliverydistance, preparationtime, temp,precip
df.orders_avg = aggregate(df.orders[,c(7,8,11,12,13,15)],by=list(df.orders$vendor_id), FUN=mean)
df.orders_avg

#Calculate Totals of item_count,	grand_total
df.orders_sum = aggregate(df.orders[,c(16,17,18)],by=list(df.orders$vendor_id), FUN=sum)
df.orders_sum

#Merged order aggregates and vendors using vendor_id as join key
df.merged = inner_join(inner_join(df.vendors,
                        df.orders_avg,
                        by = c("id" = "Group.1")),
                        df.orders_sum,
                        by = c("id" = "Group.1"))
df.merged

#Export merged dataset
#write.csv(df.merged,"./data/vendors_orders_merged.csv", row.names = FALSE)

```

```{r}

# Create a linear model using all attributes. Outcome variable: revenue
lm_revenue = lm(revenue ~ vendor_category_id+delivery_charge+serving_distance+prepration_time
+discount_percentage+vendor_rating+total_items+deliverydistance+preparationtime+temp+precip+rated_vendor+delivery_time+Loc_Home+Loc_Work+Loc_Other, data = df.merged)

# Apply step wise analysis to determine the most significant features
summary(step(lm_revenue))

```
Let’s create a linear model using the most important attributes relevant to revenue as the outcome variable; Loc_Other, vendor_category_id, vendor_rating, preparationtime, temp.

```{r}

# Create a linear model using the most important attributes
lm_revenue.final = lm(revenue~Loc_Other+vendor_category_id+vendor_rating+preparationtime+temp+Loc_Home, data=df.merged)
summary(lm_revenue.final)

# Take a look at r squared values to determine quality of fit
summary(lm_revenue.final)$r.squared
summary(lm_revenue.final)$adj.r.squared

```
```{r}

# Create a linear model using all attributes. Outcome variable: vendor_rating
lm_vendor_rating = lm(vendor_rating ~ vendor_category_id+delivery_charge+serving_distance+prepration_time+discount_percentage+total_items+deliverydistance+preparationtime+temp+precip+delivery_time+Loc_Home+Loc_Work+Loc_Other, data = df.merged)

# Apply step wise analysis to determine the most significant features
summary(step(lm_vendor_rating))

```
Multiple R-squared:  0.1635,	Adjusted R-squared:  0.1267 

The R-Squared values of the stepwise regression model with vendor_rating as the outcome variable is extremely low implying that the model is not a good fit.

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

